Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-02-26 WSSSPE1_report/WSSSPE1_summary_report.tex
use WSSSPE1 in title and abstract (not just WSSSPE)

\title[]{Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)}

@@

\begin{abstract}
This technical report discusses the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE). ...
\end{abstract}

>>>>

\title[]{Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)}

@@

\begin{abstract}
This technical report discusses the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1). ...
\end{abstract}
